%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[caption=false,font=footnotesize]{subfig}
\frenchspacing

\begin{document}
\title{LIDAR to Image Coregistration Using Orbital Data}
\author{Brian Coltin and Ara Nefian}
\maketitle
\begin{abstract}
\begin{quote}
In 2009, the Lunar Reconnaissance Orbiter (LRO) launched with the Lunar Orbiter Laser
Altimeter (LOLA), an instrument that precisely measures the distance to the Moon's
surface. The LOLA data is recorded in tracks tracing the LRO's orbit above the Moon,
consisting of "shots" of five distance measurements each. In this work, we seek to
coregister these tracks to images taken during the Apollo program to form a consistent
map of the moon, merging both data sources. The coregistration problem is challenging
due to significant uncertainty in both spacecrafts' positions. We introduce an algorithm
to coregister the LOLA data to the Apollo images. First, we compute each LOLA shot's
surface normal and, from this normal and the approximate LRO and sun positions,
estimate the lunar albedo. We then perform a local brute-force search comparing the
estimated albedo to a low-resolution Apollo image to find a coarse alignment. Finally,
we use the Gauss-Newton algorithm to precisely align the LOLA tracks to progressively
higher resolution layers of the image pyramid.
\end{quote}
\end{abstract}

\section{Introduction}
\input{introduction.tex}
\section{Related Work}
\input{related.tex}
\section{Problem Statement}
\input{problem.tex}
\section{Aligning LIDAR to Images}
\input{alignment.tex}
\section{Selected Results}
\input{results.tex}
\section{Conclusion}
\input{conclusion.tex}

\bibliographystyle{plain}
\bibliography{biblio}

\end{document}

